The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-24 Writeup/paper_v3.tex
figure 6 caption

% \rachel{As we discussed, you should get rid of the early parts of this
%   regarding second moments, and replace it with a brief description of
%   what shape estimates we use from GalSim (re-Gaussianization).}
% 
% {\bf Should explain in brief Claire's work.} \\
\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{sample_histograms}
 \caption{The distributions of the morphological parameters of interest, namely the distortion, \sersic index and \btt are presented. 
          The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited
          samples, as discussed in
          Sec.~\ref{sub:volumelimiting}. 
%           \rachel{I am confused by the
%             top line: first, distortion is $(1-q^2)/(1+q^2)$, not
%             $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
%           plotting - from Claire or from re-Gaussianization.  It seems
%         redundant to have two plots of the same thing, so I hope that
%         one is from Claire and one from re-Gaussianization, but these
%         needs to be indicated clearly.  Finally, we have the option of
%       deliberately plotting different things (like $q$ from Claire
%       vs. distortion from re-Gaussianization) or explicitly choosing
%       to plot the same thing (like total distortion from Claire
%       vs. total distortion from re-Gaussianization).  I'm not sure
%       which is best; the latter would allow a comparison between the
%       two types of shape estimates, which could be interesting, so I'm
%       inclined to say you should do that.}} \arun{Done.}
  }
  \label{fig:sample_histograms}
\end{figure*}

>>>>

% \rachel{As we discussed, you should get rid of the early parts of this
%   regarding second moments, and replace it with a brief description of
%   what shape estimates we use from GalSim (re-Gaussianization).}
% 
% {\bf Should explain in brief Claire's work.} \\
\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{sample_histograms}
 \caption{The distributions of the morphological parameters of interest, namely the distortion (top left, from \sersic fits, and top right, from re-Gaussianization), \sersic index (bottom left) and bulge-to-total ratio (bottom right) are presented. 
          The shapes of these distributions depend on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited
          samples, as discussed in
          Sec.~\ref{sub:volumelimiting}. 
%           \rachel{I am confused by the
%             top line: first, distortion is $(1-q^2)/(1+q^2)$, not
%             $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
%           plotting - from Claire or from re-Gaussianization.  It seems
%         redundant to have two plots of the same thing, so I hope that
%         one is from Claire and one from re-Gaussianization, but these
%         needs to be indicated clearly.  Finally, we have the option of
%       deliberately plotting different things (like $q$ from Claire
%       vs. distortion from re-Gaussianization) or explicitly choosing
%       to plot the same thing (like total distortion from Claire
%       vs. total distortion from re-Gaussianization).  I'm not sure
%       which is best; the latter would allow a comparison between the
%       two types of shape estimates, which could be interesting, so I'm
%       inclined to say you should do that.}} \arun{Done.}
  }
  \label{fig:sample_histograms}
\end{figure*}
